---
format: 
  revealjs:
    navigation-mode: vertical
    slide-number: false
    width: 1600
    height: 900
    logo: "images/revelo.png"
    footer: "[home page](https://mchiapello.github.io/202304_REVELO_Torvergata/)"
    css: ["css/theme.css", "css/custom.css"]
    theme: simple
    controls: true
editor: source
filters:
  - roughnotation
editor_options: 

  chunk_output_type: inline
---

##  {#TitleSlide data-menu-title="TitleSlide" background-image="images/back001.jpg" background-size="cover" background-opacity="0.3"}

```{r setup, include=FALSE}
library(fontawesome)
library(tidyverse)
library(quarto)
library(gt)
library(gtExtras)
library(gtsummary)
```

<style>
  @import url('https://fonts.googleapis.com/css2?family=Architects+Daughter&family=Julius+Sans+One&family=Montserrat:wght@300&family=Rock+Salt&display=swap');
</style>

::: {style="position: absolute; left: 180px; top: 200px; height: 525px; width: 1500px; background-color: #69b1e9; padding: 20px; padding-left: 50px; border-radius: 5px;"}
[Introduzione al Corso]{style="font-size: 120px; font-weight: bold; line-height: 1em; margin: 0px; font-family: 'Architects Daughter', cursive;"}

[Introduzione all'analisi RNASeq in R]{style="font-size: 40px;font-weight: bold;"}

[Dipartimento di Biomedicina e Prevenzione]{style="font-size: 40px;font-weight: bold;"}

<br> <br>

[Marco Chiapello, Revelo Datalab]{style="font-size: 40px; font-weight: bold;"}

[2023-03-31]{style="font-size: 30px;font-weight: bold;"}
:::


#  {background-image="images/back001.jpg" background-size="cover" background-opacity="0.3"}

[Code of Conduct]{.tit .p-span-center}

[{{< fa people-group >}}]{.icon .p-span-center}

##  {background-image="images/back001.jpg" background-size="cover" background-opacity="0.3"}

::: {style="font-size: 40px; text-align: justify"}
We are dedicated to providing a [welcoming]{.rn} and [supportive]{.rn} environment for all people, [regardless of background or identity]{.rn rn-type="box" rn-color="black"}.

By participating in this course, [participants accept the Code of Conduct]{.rn}.

Any form of behaviour to [exclude]{.rn rn-color="orange"}, [intimidate]{.rn rn-color="orange"}, or [cause discomfort]{.rn rn-color="orange"} is a violation of the Code of Conduct. In order to foster a [positive and professional learning environment]{.rn rn-color="green"} we encourage the following kinds of behaviours in all platforms and events:

::: {.fragment .fade-up}
-   Use welcoming and inclusive language
:::

::: {.fragment .fade-up}
-   Be respectful of different viewpoints and experiences
:::

::: {.fragment .fade-up}
-   Gracefully accept constructive criticism
:::

::: {.fragment .fade-up}
-   Focus on what is best for the community
:::

::: {.fragment .fade-up}
-   Show courtesy and respect towards other community members
:::
:::

#  {background-image="images/back002.jpg" background-size="cover" background-opacity="0.3"}

[Presentiamoci]{.tit .p-span-center}

[{{< fa id-card >}}]{.icon .p-span-center}

##  {background-image="images/back002.jpg" background-size="cover" background-opacity="0.3"}

::: {.fragment .fade-down style="font-size: 100px; text-align: start;"}
{{< fa 1 >}} Chi sei?
:::

<br>

::: {.fragment .fade-down style="font-size: 100px; text-align: start; margin-left: 200px"}
{{< fa 2 >}} Cosa hai studiato?
:::

<br>

::: {.fragment .fade-down style="font-size: 100px; text-align: start;"}
{{< fa 3 >}} Quali sono i tuoi obiettivi?
:::

<br>

::: {.fragment .fade-down style="font-size: 100px; text-align: start; margin-left: 200px"}
{{< fa 4 >}} Quali sono le aspettative per il corso?
:::

#  {background-image="images/website.png" background-size="cover" background-opacity="0.1"}

[Com'è strutturato il corso]{.tit .p-span-center}

##  {background-image="images/website.png" background-size="cover" background-opacity="0.1"}

[Website]{.p-span-center style="font-size: 100px"}

::: {.fragment .fade-down .p-img-center}
```{r}
#| echo: false
#| layout-ncol: 1
plot(qrcode::qr_code("https://mchiapello.github.io/202304_REVELO_Torvergata/"))
```

[http://bit.ly/3ZcDcj9]{.p-span-center style="font-size: 100px; font-weight: bold;"}
:::

##  {background-image="images/website.png" background-size="cover" background-opacity="0.1"}

[Agenda]{.p-span-center style="font-size: 100px"}

::: columns
::: {.column width="50%"}
[Primo Giorno]{.p-span-center}
[Teoria]{.p-span-center}

<br>

:::{.fragment .fade-rigth fragment-index=1}

[Orari]{style="font-weight: bold;"}    
9:30 : Introduzione al Corso   
10:00: Riepilogo R             
10:45: Pausa                   
11:00: Introduzione all'RNASeq


12:30: Pausa pranzo            


13:30: Ricerca Riproducibile       
14:45: Pausa                   
15:00: Software and code       
16:30: Considerazioni finali   

:::
:::

::: {.column width="50%"}
[Secondo Giorno]{.p-span-center}
[Pratica]{.p-span-center}

<br>

:::{.fragment .fade-rigth fragment-index=2}
[Orari]{style="font-weight: bold;"}    
9:30 : Live Code (quantification)   
10:45: Pausa                   
11:00: Live Code (DGE)


12:30: Pausa pranzo            


13:30: Live Code (DGE)      
14:45: Pausa                   
15:00: Capstone exercise                    
16:30: Considerazioni finali   
:::
:::
:::

#  {background-image="images/website.png" background-size="cover" background-opacity="0.1"}

[Teaching system]{.tit .p-span-center}

[{{< fa chalkboard-user >}}]{.icon .p-span-center}

##  {background-image="images/website.png" background-size="cover" background-opacity="0.1"}

[Approach]{.p-span-center style="font-size: 100px"}

:::{style="font-size: 70px"}
1. Open source tools

1. Supporting community

1. Your laptop is everything you need

1. [Constant feedback]{.rn rn-index=1}

1. [Ask questions]{.rn rn-index=1}
:::

##  {background-image="images/website.png" background-size="cover" background-opacity="0.1"}

[Feedbacks]{.p-span-center style="font-size: 100px"}

- [Immediati]{style="font-size: 70px"}

  - Sticky notes

- [Formative assessment]{style="font-size: 70px"}

  - Veloci questionari o esercizi

- [Alla fine di ogni modulo]{style="font-size: 70px"}

  - Sticky notes

##  {background-image="images/website.png" background-size="cover" background-opacity="0.1"}

[Domande]{.p-span-center style="font-size: 100px"}

<br>
<br>

::::{style="font-size: 100px; font-family: 'Julius Sans One', sans-serif;"}
:::{.callout-tip}
## Don Lorenzo Milani

**Ogni parola che non capisci oggi è un calcio in culo domani**
:::
::::

##  {background-image="images/website.png" background-size="cover" background-opacity="0.1"}

[Strumenti]{.p-span-center style="font-size: 100px"}

- [Website]{style="font-size: 70px"}
  
- [Slack]{style="font-size: 70px"}

  - Strumento di comunicazione
  
<br>
<br>


[Entrambi rimarranno online per sempre]{.p-span-center style="font-size: 70px" .rn}

#  {background-image="images/website.png" background-size="cover" background-opacity="0.1"}

[Goals]{.tit .p-span-center}

[{{< fa bullseye >}}]{.icon .p-span-center}


##  {background-image="images/website.png" background-size="cover" background-opacity="0.1"}

[Goals]{.p-span-center style="font-size: 100px"}

::::{style="font-size: 60px; font-family: 'Julius Sans One', sans-serif;"}

:::{.fragment .fade-in fragment-index=1}
::: {.fragment .semi-fade-out fragment-index=2}
1. Become a better data scientist
:::
:::

:::{.fragment .fade-in fragment-index=2}
::: {.fragment .semi-fade-out fragment-index=3}
1. Leanr best practices for working with R/Bioconductor
:::
:::

:::{.fragment .fade-in fragment-index=3}
::: {.fragment .semi-fade-out fragment-index=4}
1. Understand how to do RNASeq bulk data analysis
:::
:::

:::{.fragment .fade-in fragment-index=4}
::: {.fragment .semi-fade-out fragment-index=5}
1. Develop a lightweight and reusable RNASeq pipeline
:::
:::

::::

#  {background-image="images/qmark.jpg" background-size="cover" background-opacity="0.7"}


::: {style="position: absolute; left: 980px; top: 450px;"}
[Domande?]{style="font-size: 130px; font-weight: bold; color: white"}
:::

# {background-image="images/notice001.jpg" background-size="cover" background-opacity="0.8"}

:::{.fragment .fade-in}
:::{style="color: white; font-family: 'Rock Salt', cursive; font-size: 60px"}
Tutto 

in questo corso 

è stato fatto in [R]{style="font-size: 80px"}
:::
:::
